Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-23 writing/CONUS_AOD.qmd
Corrected the computation of envelope widths.

We use Nelder-Mead optimization to construct new error envelopes with coverage as close to 2/3 as possible for each of two subsets of the data: observations less than or equal to 0.6, and observations greater than 0.6. The results are an envelope with `r eee = \(pred) {o = empirical.error.envelope(obs = dt$y.ground, pred); stopifnot(o$convergence == 0); o$par}; show.eee = \(pred) {ps = eee(pred); sprintf("additive part %.03f and multiplicative part %.03f", ps[1], ps[2])}; show.eee(dt$y.sat)` for the raw satellite values, and an envelope with `r show.eee(dt$y.ground.pred)` for our predictions. The mean widths of the envelopes across all observations are `r me = \(pred) {ps = eee(pred); sprintf("%.03f", 2*ps[1] + 2*mean(dt$y.ground))}; me(dt$y.sat)` for the raw values and `r me(dt$y.ground.pred)` for our predictions. The original error envelope (reported in the AMT MAIAC publication), applied to the raw satellite values, has coverage `r x = envelope.tester(obs = dt$y.ground, pred = dt$y.sat)(.05, .1); sprintf("%.03f", x["lo"])` in the low subset and `r sprintf("%.03f", x["hi"])` in the high subset.

>>>>

We use Nelder-Mead optimization to construct new error envelopes with coverage as close to 2/3 as possible for each of two subsets of the data: observations less than or equal to 0.6, and observations greater than 0.6. The results are an envelope with `r eee = \(pred) {o = empirical.error.envelope(obs = dt$y.ground, pred); stopifnot(o$convergence == 0); o$par}; show.eee = \(pred) {ps = eee(pred); sprintf("additive part %.03f and multiplicative part %.03f", ps[1], ps[2])}; show.eee(dt$y.sat)` for the raw satellite values, and an envelope with `r show.eee(dt$y.ground.pred)` for our predictions. The mean widths of the envelopes across all observations are `r me = \(pred) {ps = eee(pred); sprintf("%.03f", 2*ps[1] + 2*ps[2]*mean(dt$y.ground))}; me(dt$y.sat)` for the raw values and `r me(dt$y.ground.pred)` for our predictions. The original error envelope (reported in the AMT MAIAC publication), applied to the raw satellite values, has coverage `r x = envelope.tester(obs = dt$y.ground, pred = dt$y.sat)(.05, .1); sprintf("%.03f", x["lo"])` in the low subset and `r sprintf("%.03f", x["hi"])` in the high subset.
